Level-Set method on \texttt{p4est}

### 2015-06-19 paper/tex/conclusion.tex
final pass (mohammad+frederic+arthur) done. One last thing remains, scaling with large number of processes and for a heavier load
Level set method and acknowledgement

\section*{Acknowledgment} 
The funding for this project was provided by \mohammad{the funding agency}. We would also like to thank the technical staff at the Texas Advanced Computing Center (TACC) and the developer community of PETSc library for their valuable suggestions during this project.

>>>>

\section*{Acknowledgment} 
The funding for this project was provided by ONR N00014-11-1-0027.
We would also like to thank the technical staff at the Texas Advanced Computing
Center (TACC) and the developer community of PETSc library for their valuable
suggestions during this project.
The third author acknowledges support by the Hausdorff Center for Mathematics
(HCM) at Bonn University,
% and the Transregio 32 research collaborative, both
an initiative funded by the German Research Foundation (DFG).

### 2015-06-19 paper/tex/levelset_method.tex
Level set method and acknowledgement

In general, an infinite number of level-set functions can describe the same zero contour and thus an interface. However, it is desirable to chose a function with the signed distance property $|\underline{\nabla} \phi| = 1$. As detailed in section \ref{sec:introduction}, we solve the pseudo-time transient reinitialization equation \cite{Sussman;Smereka;Osher:94:A-Level-Set-Approach, Osher;Fedkiw:01:Level-Set-Methods:-A} to achieve this property,
\be
\phi_\tau + S(\phi_0)\left(\lvert \underline{\nabla} \phi \rvert - 1\right) = 0,
\label{eq:reinitialization}
\ee
where $\tau$ is a pseudo time step, $\phi_0$ is any level-set function that correctly describes the interface location and $S(\phi_0)$ is an approximation of the sign function. Here, we do not go into the details of the sequential algorithms for solving equations \eqref{eq:ls} and \eqref{eq:reinitialization}. Instead, we note that the algorithms presented in section \ref{sec:parallel algorithms} are based on the sequential methods presented in \cite{Min;Gibou:07:A-second-order-accur} and refer the interested reader to the aforementioned articles and references therein for more details.

>>>>

In general, an infinite number of level-set functions can describe the same
zero contour and thus the same interface.
However, it is desirable to choose a function with the signed distance property
$|\underline{\nabla} \phi| = 1$. As detailed in section \ref{sec:introduction},
we solve the pseudo-time transient reinitialization equation
\cite{Sussman;Smereka;Osher:94:A-Level-Set-Approach,
Osher;Fedkiw:01:Level-Set-Methods:-A} to achieve this property,
\be
\phi_\tau + S(\phi_0)\left(\lvert \underline{\nabla} \phi \rvert - 1\right) = 0,
\label{eq:reinitialization}
\ee
where $\tau$ is a pseudo time step, $\phi_0$ is any level-set function that correctly describes the interface location and $S(\phi_0)$ is an approximation of the sign function. Here, we do not go into the details of the sequential algorithms for solving equations \eqref{eq:ls} and \eqref{eq:reinitialization}.
Instead, we note that the parallel algorithms presented in section \ref{sec:parallel
algorithms} are based on the sequential methods presented earlier in
\cite{Min;Gibou:07:A-second-order-accur} and refer the interested reader to the
aforementioned articles and references therein for more details.
